--- 
title: "Clinical epidemiology with R"
author: "James Brophy"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output:
  bookdown::gitbook:
    highlight: tango
    includes:
      in_header: style.css
  bookdown::pdf_book:
    keep_tex: yes
bookdown::html_book:
  theme: cerulean
  css: style.css
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: brophyj/epi_book
description: "This is an intermediate epidemiology book that focuses on clinical epidmeiology and its quantification using R. It stems from my belief that the learning of epidmeiologic principles is consolidated through hands on coding examples."
---

```{r eval=FALSE, include=FALSE}
install.packages("bookdown")
install.packages("webshot")
webshot::install_phantomjs()
# or the development version
# devtools::install_github("rstudio/bookdown")

```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown', 'ggplot2', 'tidyverse', 'epiR'), 'packages.bib')
```

# About the Author {-}


Jay Brophy is a full professor with a joint appointment in the Departments of Medicine and Epidemiology and Biostatistics at McGill University where he works as a clinical cardiologist and does research in cardiovascular epidemiology. His research interests are eclectic and include outcomes research, pharmacoepidemiology, health technology assessment, economic analyses and clinical research.   

<!--chapter:end:index.Rmd-->


# Introduction {#intro}

Placeholder



<!--chapter:end:01-intro.Rmd-->


# Introduction to statistical software - R 

Placeholder


## Statistical software - R
## R - Common data and variable manipulations
## R - More than a statistical program 
## R - General Public License

<!--chapter:end:02-intro_R.Rmd-->


# About the Author {-}

Placeholder


## Statistical software - R
## R - Common data and variable manipulations
## R - More than a statistical program 
## R - General Public License
## Statistical software - R
## R - Common data and variable manipulations
## R - More than a statistical program 
## R - General Public License
## Statistical software - R
## R - Common data and variable manipulations
## R - More than a statistical program 
## R - General Public License

<!--chapter:end:X_main.Rmd-->

